Software Citation Principles

### 2016-04-17 sc-principles/software-citation-principles.tex
Reordered use case table columns. Addresses #126.
Shifted stakeholder column to far right. Also clarified that stakeholders are examples.

\newcommand*\rot[1]{\begin{turn}{90} #1 \end{turn}}%
\rowcolors{4}{gray!25}{white}
\begin{table}[tbhp]
\caption{Use cases and basic metadata requirements for software citation, adapted from~\cite{SC-Use-Cases}.}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c c@{}}
\toprule
 & & \multicolumn{9}{c}{Requirements} \\
 \cmidrule{3-11}
Stakeholder & wants to 	& \rot{Unique identifier} &  \rot{Software name} & \rot{Author(s)} & \rot{Contributor role} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Indexed citations} & \rot{Software license}  \\
\midrule
Researcher            & 1.\ use someone else's software for a paper      & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Researcher            & 2.\ use someone else's software for new software & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 3.\ contribute to software                   & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 4.\ find citations of software               & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Researcher            & 5.\ get credit for software development      & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 6.\ ``reproduce'' analysis                   & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 7.\ benchmark software                       & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet \\
Researcher            & 8.\ find software to implement task          & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet & \textbullet & \textbullet \\
Publisher             & 9.\ publish software paper                   & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             \\
Publisher             & 10.\ publish papers that cite software        & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
Indexer               & 11.\ build catalog of software                & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet \\
Domain group\slash library\slash archive          & 12.\ build software catalog\slash registry                & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet &             &             \\
Repository            & 13.\ show scientific impact of holdings       & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Funder                & 14.\ show how funded software has been used   & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             \\
Evaluator             & 15.\ evaluate contributions of researcher     & \textbullet &             & \textbullet & \textbullet &             & \textbullet &             & \textbullet &             \\
Citation manager      & 16.\ store software entry        			 & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%

>>>>

\newcommand*\rot[1]{\begin{turn}{90} #1 \end{turn}}%
\rowcolors{4}{gray!25}{white}
\begin{table}[tbhp]
\caption{Use cases and basic metadata requirements for software citation, adapted from~\cite{SC-Use-Cases}.}
\centering
\scriptsize\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{@{}l l c c c c c c c c l@{}}
\toprule
 & \multicolumn{9}{c}{Requirements} & \\
 \cmidrule{2-10}
Use case 	& \rot{Unique identifier} &  \rot{Software name} & \rot{Author(s)} & \rot{Contributor role} & \rot{Version number} & \rot{Release date} & \rot{Location\slash repository} & \rot{Indexed citations} & \rot{Software license} & Example stakeholder(s) \\
\midrule
1.\ Use software for a paper                     & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             & Researcher \\
2.\ Use software in\slash with new software      & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             & \textbullet & Researcher \\
3.\ Contribute to software                       & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & Researcher \\
4.\ Find citations of software                   & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             & Researcher \\
5.\ Get credit for software development          & \textbullet & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet &             & \textbullet & Researcher \\
6.\ ``Reproduce'' analysis                       & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet & Researcher \\
7.\ Benchmark software                           & \textbullet & \textbullet &             &             & \textbullet & \textbullet & \textbullet &             & \textbullet & Researcher \\
8.\ Find software to implement task              & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet & \textbullet & \textbullet & Researcher \\
9.\ Publish software paper                       & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet &             &             & Publisher \\
10.\ Publish papers that cite software           & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             & Publisher \\
11.\ Build catalog of software                   & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet & \textbullet & Indexer \\
12.\ Build software catalog\slash registry       & \textbullet & \textbullet & \textbullet &             &             &             & \textbullet &             &             & Domain group\slash library\slash archive \\
13.\ Show scientific impact of holdings          & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             & Repository \\
14.\ Show how funded software has been used      & \textbullet & \textbullet &             &             &             &             &             & \textbullet &             & Funder \\
15.\ Evaluate contributions of researcher        & \textbullet &             & \textbullet & \textbullet &             & \textbullet &             & \textbullet &             & Evaluator \\
16.\ Store software entry                        & \textbullet & \textbullet & \textbullet &             & \textbullet & \textbullet & \textbullet & \textbullet &             & Citation manager \\
\bottomrule
\end{tabular}
\label{tab:use_cases}
\end{table}%
